---
title: "HOMEWORK1"
output: github_document

---
#Problem 1
```{r}
library(tidyverse)
  vec_numeric = rnorm(8)
  vec_logical = vec_numeric > 0
  vec_char = c("a","a","a","a","a","a","a","")
  vec_factor = factor(c("a","a","b","b","b","c","c","c"))
hm1_df = tibble(
  vec_numeric,
  vec_logical,
  vec_char,
  vec_factor
)

mean(hm1_df$vec_numeric)
mean(hm1_df$vec_logical)
mean(hm1_df$vec_char)
mean(hm1_df$vec_factor)
```
The numeric vector and logical vector work but character and factor vector don't work.
```{r, eval = FALSE}
num_log = as.numeric(vec_logical) 
num_char = as.numeric(vec_char) 
num_factor = as.numeric(vec_factor)

```
The "False" of the logical vector became "0", the "TRUE" of the logical vector became "1". And we cannot change character vector into numeric vector. The factor vector is changed to numeric vector by its levels.
```{r}

as.numeric(vec_logical) * vec_numeric
as.factor(vec_logical) * vec_numeric
as.numeric(as.factor(vec_logical)) * vec_numeric
```
#Problem 2
Create a data frame

```{r}
x = rnorm(500)
y = rnorm(500)
log_pro2 = x + y > 1
num_pro2 = as.numeric(log_pro2)
fac_pro2 = as.factor(log_pro2)
pro2_df = tibble(
  x,y,log_pro2,num_pro2,fac_pro2
)

```
Write a short description of your vector

the size of the dataset is row = `r nrow(pro2_df)` and col = `r ncol(pro2_df)`

the mean of x is `r mean(x)`

the median of x is `r median(x)`

the standard deviation of x is `r sd(x)`

the proportion of cases for which x + y > 1 is `r length(log_pro2[[TRUE]])/length(x)`

```{r}
#Make a scatterplot
scatterplot1 = ggplot(pro2_df, aes(x = x, y = y,color = log_pro2)) + geom_point()
scatterplot2 =ggplot(pro2_df, aes(x = x, y = y,color = num_pro2)) + geom_point()
scatterplot3 =ggplot(pro2_df, aes(x = x, y = y,color = fac_pro2)) + geom_point()
scatterplot1
scatterplot2
scatterplot3

ggsave("scatterplot1.pdf", scatterplot1) # Export your first scatterplot to your project directory using ggsave
```
The scatterplot using logical vector as its color and that using factor vector as its color have the same results, both according to "TRUE" and "FALSE". The scatterplot using numeric vector as its color as scales from 0 to 1.
